---
title: "Compilation"
author: "ags"
date: "03-02-2021"
output:
  html_document:
    code_folding: hide
    fig_height: 6
    fig_width: 8
    theme: spacelab
    toc: yes
    toc_depth: 6
    toc_float: yes
    number_sections: yes
---

<style type="text/css">
.tablelines table, .tablelines td, .tablelines th {
  border: 1px solid black;
  }
.centrado {
  text-align: center;
}
.table.center {
  margin-left:auto; 
  margin-right:auto;
}
.table_wrapper{
  display: block;
  overflow-x: auto;
  white-space: nowrap;
}
code.r{
  font-size: 8px;
}
body{ /* Normal  */
    text-align: justify;
}
.superbigimage{
  overflow-y:scroll;
  white-space: nowrap;
}
.superbigimage img{
  overflow-y: scroll;
  overflow-x: hidden;
}
p.comment {
  background-color: #FF7F79;
    padding: 10px;
  border: 1px solid black;
  margin-left: 25px;
  border-radius: 5px;
  font-style: italic;
}
</style>

<style>
  p.comment {
    background-color: #ff9a9a;
      padding: 10px;
    border: 1px solid red;
    margin-left: 25px;
    border-radius: 5px;
    font-style: italic;
  }

</style>

------------------------------------------------------------------------

```{r setup1, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
rm(list=ls());gc()

unlink('BD_Compilation_cache', recursive = TRUE)

if(!require(here)){install.packages("here")}

#if(!require(groundhog)){install.packages("groundhog")}
answer <- "OK"
consent <- TRUE
#require(groundhog)
#library(groundhog)
#set.groundhog.folder(here::here())


#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

try_with_time_limit <- function(expr, cpu = Inf, elapsed = Inf)
{
  y <- try({setTimeLimit(cpu, elapsed); expr}, silent = TRUE) 
  if(inherits(y, "try-error")) NULL else y 
}
eval_fork <- function(..., timeout=60){

  #this limit must always be higher than the timeout on the fork!
  setTimeLimit(timeout+5);      

  #dispatch based on method
  ##NOTE!!!!! Due to a bug in mcparallel, we cannot use silent=TRUE for now.
  myfork <- parallel::mcparallel({
    eval(...)
  }, silent=FALSE);

  #wait max n seconds for a result.
  myresult <- parallel::mccollect(myfork, wait=FALSE, timeout=timeout);

  #try to avoid bug/race condition where mccollect returns null without waiting full timeout.
  #see https://github.com/jeroenooms/opencpu/issues/131
  #waits for max another 2 seconds if proc looks dead 
  while(is.null(myresult) && totaltime < timeout && totaltime < 2) {
     Sys.sleep(.1)
     enddtime <- Sys.time();
     totaltime <- as.numeric(enddtime - starttime, units="secs")
     myresult <- parallel::mccollect(myfork, wait = FALSE, timeout = timeout);
  }

  #kill fork after collect has returned
  tools::pskill(myfork$pid, tools::SIGKILL);    
  tools::pskill(-1 * myfork$pid, tools::SIGKILL);  

  #clean up:
  parallel::mccollect(myfork, wait=FALSE);

  #timeout?
  if(is.null(myresult)){
    stop("R call did not return within ", timeout, " seconds. Terminating process.", call.=FALSE);      
  }

  #move this to distinguish between timeout and NULL returns
  myresult <- myresult[[1]];

  #reset timer
  setTimeLimit();     

  #forks don't throw errors themselves
  if(inherits(myresult,"try-error")){
    #stop(myresult, call.=FALSE);
    stop(attr(myresult, "condition"));
  }

  #send the buffered response
  return(myresult);  
}
```
```{r setup2}
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})

`%>%` <- magrittr::`%>%`

copy_names <- function(x,row.names=FALSE,col.names=TRUE,dec=",",...) {
  if(class(ungroup(x))[1]=="tbl_df"){
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)    
        }
  } else {
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)       
  }
 }
}  

if(!require(pacman)){install.packages("pacman")}

pacman::p_unlock(lib.loc = .libPaths()) #para no tener problemas reinstalando paquetes
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

#get.snowball(c("readr","RODBC","foreign","dplyr","tidyverse","lubridate"), "2020-02-01")
#groundhog.library('nlme','2021-01-01')
#groundhog.library('Matrix','2021-01-01')
#groundhog.library('MASS','2021-01-01')
#try_with_time_limit(groundhog.library("dplyr", "2020-11-01", ignore.deps = c("digest","generics", "glue", "magrittr", "pillar", "R6", "rlang", "tibble", "vctrs")))
#try_with_time_limit(groundhog.library("foreign", "2021-01-01"))
#try_with_time_limit(groundhog.library("readr", "2021-01-01"))
#try_with_time_limit(groundhog.library("RODBC", "2021-01-01"))

#try_with_time_limit(groundhog.library("tidyverse", "2021-01-01"))
#try_with_time_limit(groundhog.library("lubridate", "2021-01-01"))

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

if(!require(dplyr)){install.packages("dplyr")}
if(!require(foreign)){install.packages("foreign")}
if(!require(readr)){install.packages("readr")}
if(!require(RODBC)){install.packages("RODBC")}
if(!require(tidyverse)){install.packages("tidyverse")}
if(!require(zoo)){install.packages("zoo")}
if(!require(tidyr)){install.packages("tidyr")}
if(!require(sjPlot)){install.packages("sjPlot")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(compareGroups)){install.packages("compareGroups")}
```

# Compile Database

## Unite Databases

We merge the datasets of yearly Urgency Admissions from 2015 to 2019, selecting the following causes (`Idcausa`):

a.  Total Consultations (1)
b.  Respiratory Consultations (2)
c.  Circulatory Consultations (12)
d.  Diarrhea Consultations (29)
e.  Trauma Consultations (18)
f.  Total Hospitalizations (25)
g.  Respiratory Hospitalizations (7)
h.  Circulatory Hospitalizations (22)
i.  Trauma Hospitalizations (23)

We selected the following healthcare institutions (`codigo_antiguo`) within 3KM:

-   Complejo Hospitalario San José (09-100)
-   Hospital de Urgencia Asistencia Pública (11-195)
-   Hospital del Salvador de Santiago (12-100)

```{r 1 - Urg15_3 Data Creation}
# -------- Access Data --------
#rm(list=setdiff(ls(), "dt"))
establecimientos <-
  readr::read_delim("establecimientos.csv",
             ";",
             escape_double = FALSE,
             trim_ws = TRUE)

target <- tempfile()
file.path(target)
unzip(paste0(getwd(), '/',"AtencionesUrg_15.zip"), exdir = target)
f <- list.files(target, pattern = ".mdb")
d5 <- RODBC::odbcConnectAccess2007(file.path(target, f))
#d5 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2015.mdb")
urg_2015 <- sqlFetch(d5, "Atenciones Urgencia 2015")
odbcClose(d5)
unlink(target)

# -------- Clean urg_2015 Columns --------
urg_2015$idestablecimiento <- urg_2015$IdEstablecimiento
urg_2015$Col01 <- urg_2015$Total
urg_2015$Col02 <- urg_2015$`Menores de 1 año`
urg_2015$Col03 <- urg_2015$`1-4 años`
urg_2015$Col04 <- urg_2015$`5-14 años`
urg_2015$Col05 <- urg_2015$`15-64 años`
urg_2015$Col06 <- urg_2015$`65 años y más`
urg_2015$Idcausa <- urg_2015$IdCausa
# -------- Establish Hospital ID Codes --------
estab_id <-
  establecimientos[establecimientos$codigo_antiguo == "09-100" |
                     establecimientos$codigo_antiguo == "11-195" |
                     establecimientos$codigo_antiguo == "12-100", "codigo_antiguo", drop =
                     TRUE]
estab_id <- as.factor(estab_id)
columns = c("idestablecimiento",
            "Col01",
            "Col02",
            "Col03",
            "Col04",
            "Col05",
            "Col06",
            "fecha")

# -------- Create Consultation Columns --------
cons_total <-
  urg_2015[urg_2015$Idcausa == 1 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_total) <-
  c (
    "id",
    "cons_total_all",
    "cons_total_a1",
    "cons_total_1a4",
    "cons_total_5a14",
    "cons_total_15a64",
    "cons_total_65a",
    "date"
  )
cons_resp <-
  urg_2015[urg_2015$Idcausa == 2 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_resp) <-
  c (
    "id",
    "cons_resp_all",
    "cons_resp_a1",
    "cons_resp_1a4",
    "cons_resp_5a14",
    "cons_resp_15a64",
    "cons_resp_65a",
    "date"
  )
cons_circ <-
  urg_2015[urg_2015$Idcausa == 12 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_circ) <-
  c (
    "id",
    "cons_circ_all",
    "cons_circ_a1",
    "cons_circ_1a4",
    "cons_circ_5a14",
    "cons_circ_15a64",
    "cons_circ_65a",
    "date"
  )
cons_diarrea <-
  urg_2015[urg_2015$Idcausa == 29 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_diarrea) <-
  c (
    "id",
    "cons_diarrea_all",
    "cons_diarrea_a1",
    "cons_diarrea_1a4",
    "cons_diarrea_5a14",
    "cons_diarrea_15a64",
    "cons_diarrea_65a",
    "date"
  )

cons_trauma <-
  urg_2015[urg_2015$Idcausa == 18  &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_trauma) <-
  c (
    "id",
    "cons_trauma_all",
    "cons_trauma_a1",
    "cons_trauma_1a4",
    "cons_trauma_5a14",
    "cons_trauma_15a64",
    "cons_trauma_65a",
    "date"
  )

# -------- Create Hospitalization Columns --------
hosp_total <-
  urg_2015[urg_2015$Idcausa == 25 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_total) <-
  c (
    "id",
    "hosp_total_all",
    "hosp_total_a1",
    "hosp_total_1a4",
    "hosp_total_5a14",
    "hosp_total_15a64",
    "hosp_total_65a",
    "date"
  )
hosp_resp <-
  urg_2015[urg_2015$Idcausa == 7 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_resp) <-
  c (
    "id",
    "hosp_resp_all",
    "hosp_resp_a1",
    "hosp_resp_1a4",
    "hosp_resp_5a14",
    "hosp_resp_15a64",
    "hosp_resp_65a",
    "date"
  )
hosp_circ <-
  urg_2015[urg_2015$Idcausa == 22 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_circ) <-
  c (
    "id",
    "hosp_circ_all",
    "hosp_circ_a1",
    "hosp_circ_1a4",
    "hosp_circ_5a14",
    "hosp_circ_15a64",
    "hosp_circ_65a",
    "date"
  )
hosp_trauma <-
  urg_2015[urg_2015$Idcausa == 23 &
             urg_2015$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_trauma) <-
  c (
    "id",
    "hosp_trauma_all",
    "hosp_trauma_a1",
    "hosp_trauma_1a4",
    "hosp_trauma_5a14",
    "hosp_trauma_15a64",
    "hosp_trauma_65a",
    "date"
  )

# -------- Merge Columns Into One Dataset --------
cons <- merge(cons_total, cons_resp)
cons <- merge(cons, cons_circ)
cons <- merge(cons, cons_diarrea)
cons <- merge(cons, cons_trauma)

hosps <- merge(hosp_total, hosp_resp)
hosps <- merge(hosps, hosp_circ)
hosps <- merge(hosps, hosp_trauma)

urg15_3 <- merge(cons, hosps)

# -------- Write CSV File --------
#write_csv(urg15_3, "urg15_3.csv")
```

```{r 1 - Urg16_3 Data Creation}
# -------- Access Data --------
#rm(list=setdiff(ls(), "dt"))
establecimientos <-
  readr::read_delim("establecimientos.csv",
             ";",
             escape_double = FALSE,
             trim_ws = TRUE)

target <- tempfile()
file.path(target)
unzip(paste0(getwd(), '/',"AtencionesUrg_16.zip"), exdir = target)
f <- list.files(target, pattern = ".mdb")
d6 <- RODBC::odbcConnectAccess2007(file.path(target, f))
#d5 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2015.mdb")
urg_2016 <- sqlFetch(d6, "Atenciones Urgencia 2016")
odbcClose(d6)
unlink(target)


# -------- Clean urg_2016 Columns --------
urg_2016$idestablecimiento <- urg_2016$IdEstablecimiento
urg_2016$Col01 <- urg_2016$Total
urg_2016$Col02 <- urg_2016$`Menores de 1 año`
urg_2016$Col03 <- urg_2016$`1-4 años`
urg_2016$Col04 <- urg_2016$`5-14 años`
urg_2016$Col05 <- urg_2016$`15-64 años`
urg_2016$Col06 <- urg_2016$`65 años y más`
urg_2016$Idcausa <- urg_2016$IdCausa


# -------- Establish Hospital ID Codes --------
estab_id <-
  establecimientos[establecimientos$codigo_antiguo == "09-100" |
                     establecimientos$codigo_antiguo == "11-195" |
                     establecimientos$codigo_antiguo == "12-100", "codigo_antiguo", drop =
                     TRUE]
estab_id <- as.factor(estab_id)
columns = c("idestablecimiento",
            "Col01",
            "Col02",
            "Col03",
            "Col04",
            "Col05",
            "Col06",
            "fecha")

# -------- Create Consultation Columns --------
cons_total <-
  urg_2016[urg_2016$Idcausa == 1 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_total) <-
  c (
    "id",
    "cons_total_all",
    "cons_total_a1",
    "cons_total_1a4",
    "cons_total_5a14",
    "cons_total_15a64",
    "cons_total_65a",
    "date"
  )
cons_resp <-
  urg_2016[urg_2016$Idcausa == 2 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_resp) <-
  c (
    "id",
    "cons_resp_all",
    "cons_resp_a1",
    "cons_resp_1a4",
    "cons_resp_5a14",
    "cons_resp_15a64",
    "cons_resp_65a",
    "date"
  )
cons_circ <-
  urg_2016[urg_2016$Idcausa == 12 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_circ) <-
  c (
    "id",
    "cons_circ_all",
    "cons_circ_a1",
    "cons_circ_1a4",
    "cons_circ_5a14",
    "cons_circ_15a64",
    "cons_circ_65a",
    "date"
  )
cons_diarrea <-
  urg_2016[urg_2016$Idcausa == 29 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_diarrea) <-
  c (
    "id",
    "cons_diarrea_all",
    "cons_diarrea_a1",
    "cons_diarrea_1a4",
    "cons_diarrea_5a14",
    "cons_diarrea_15a64",
    "cons_diarrea_65a",
    "date"
  )

cons_trauma <-
  urg_2016[urg_2016$Idcausa == 18  &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_trauma) <-
  c (
    "id",
    "cons_trauma_all",
    "cons_trauma_a1",
    "cons_trauma_1a4",
    "cons_trauma_5a14",
    "cons_trauma_15a64",
    "cons_trauma_65a",
    "date"
  )

# -------- Create Hospitalization Columns --------
hosp_total <-
  urg_2016[urg_2016$Idcausa == 25 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_total) <-
  c (
    "id",
    "hosp_total_all",
    "hosp_total_a1",
    "hosp_total_1a4",
    "hosp_total_5a14",
    "hosp_total_15a64",
    "hosp_total_65a",
    "date"
  )
hosp_resp <-
  urg_2016[urg_2016$Idcausa == 7 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_resp) <-
  c (
    "id",
    "hosp_resp_all",
    "hosp_resp_a1",
    "hosp_resp_1a4",
    "hosp_resp_5a14",
    "hosp_resp_15a64",
    "hosp_resp_65a",
    "date"
  )
hosp_circ <-
  urg_2016[urg_2016$Idcausa == 22 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_circ) <-
  c (
    "id",
    "hosp_circ_all",
    "hosp_circ_a1",
    "hosp_circ_1a4",
    "hosp_circ_5a14",
    "hosp_circ_15a64",
    "hosp_circ_65a",
    "date"
  )
hosp_trauma <-
  urg_2016[urg_2016$Idcausa == 23 &
             urg_2016$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_trauma) <-
  c (
    "id",
    "hosp_trauma_all",
    "hosp_trauma_a1",
    "hosp_trauma_1a4",
    "hosp_trauma_5a14",
    "hosp_trauma_15a64",
    "hosp_trauma_65a",
    "date"
  )

# -------- Merge Columns Into One Dataset --------
cons <- merge(cons_total, cons_resp)
cons <- merge(cons, cons_circ)
cons <- merge(cons, cons_diarrea)
cons <- merge(cons, cons_trauma)

hosps <- merge(hosp_total, hosp_resp)
hosps <- merge(hosps, hosp_circ)
hosps <- merge(hosps, hosp_trauma)

urg16_3 <- merge(cons, hosps)

# -------- Write CSV File --------
#write_csv(urg16_3, "urg16_3.csv")
```

```{r 1 - Urg17_3 Data Creation}
# -------- Access Data --------
#rm(list=setdiff(ls(), "dt"))
establecimientos <-
  readr::read_delim("establecimientos.csv",
             ";",
             escape_double = FALSE,
             trim_ws = TRUE)

#d7 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2017.mdb")
#urg_2017 <- sqlFetch(d7, "Atenciones Urgencia 2017")
#odbcClose(d7)

target <- tempfile()
file.path(target)
unzip(paste0(getwd(), '/',"AtencionesUrg_17.zip"), exdir = target)
f <- list.files(target, pattern = ".mdb")
d7 <- RODBC::odbcConnectAccess2007(file.path(target, f))
#d5 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2015.mdb")
urg_2017 <- sqlFetch(d7, "Atenciones Urgencia 2017")
odbcClose(d7)
unlink(target)


# -------- Establish Hospital ID Codes --------
estab_id <-
  establecimientos[establecimientos$codigo_antiguo == "09-100" |
                     establecimientos$codigo_antiguo == "11-195" |
                     establecimientos$codigo_antiguo == "12-100", "codigo_antiguo", drop =
                     TRUE]
estab_id <- as.factor(estab_id)
columns = c("idestablecimiento",
            "Col01",
            "Col02",
            "Col03",
            "Col04",
            "Col05",
            "Col06",
            "fecha")

# -------- Create Consultation Columns --------
cons_total <-
  urg_2017[urg_2017$Idcausa == 1 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_total) <-
  c (
    "id",
    "cons_total_all",
    "cons_total_a1",
    "cons_total_1a4",
    "cons_total_5a14",
    "cons_total_15a64",
    "cons_total_65a",
    "date"
  )
cons_resp <-
  urg_2017[urg_2017$Idcausa == 2 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_resp) <-
  c (
    "id",
    "cons_resp_all",
    "cons_resp_a1",
    "cons_resp_1a4",
    "cons_resp_5a14",
    "cons_resp_15a64",
    "cons_resp_65a",
    "date"
  )
cons_circ <-
  urg_2017[urg_2017$Idcausa == 12 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_circ) <-
  c (
    "id",
    "cons_circ_all",
    "cons_circ_a1",
    "cons_circ_1a4",
    "cons_circ_5a14",
    "cons_circ_15a64",
    "cons_circ_65a",
    "date"
  )
cons_diarrea <-
  urg_2017[urg_2017$Idcausa == 29 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_diarrea) <-
  c (
    "id",
    "cons_diarrea_all",
    "cons_diarrea_a1",
    "cons_diarrea_1a4",
    "cons_diarrea_5a14",
    "cons_diarrea_15a64",
    "cons_diarrea_65a",
    "date"
  )
cons_trauma <-
  urg_2017[urg_2017$Idcausa == 18 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_trauma) <-
  c (
    "id",
    "cons_trauma_all",
    "cons_trauma_a1",
    "cons_trauma_1a4",
    "cons_trauma_5a14",
    "cons_trauma_15a64",
    "cons_trauma_65a",
    "date"
  )

# -------- Create Hospitalization Columns --------
hosp_total <-
  urg_2017[urg_2017$Idcausa == 25 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_total) <-
  c (
    "id",
    "hosp_total_all",
    "hosp_total_a1",
    "hosp_total_1a4",
    "hosp_total_5a14",
    "hosp_total_15a64",
    "hosp_total_65a",
    "date"
  )
hosp_resp <-
  urg_2017[urg_2017$Idcausa == 7 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_resp) <-
  c (
    "id",
    "hosp_resp_all",
    "hosp_resp_a1",
    "hosp_resp_1a4",
    "hosp_resp_5a14",
    "hosp_resp_15a64",
    "hosp_resp_65a",
    "date"
  )
hosp_circ <-
  urg_2017[urg_2017$Idcausa == 22 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_circ) <-
  c (
    "id",
    "hosp_circ_all",
    "hosp_circ_a1",
    "hosp_circ_1a4",
    "hosp_circ_5a14",
    "hosp_circ_15a64",
    "hosp_circ_65a",
    "date"
  )
hosp_trauma <-
  urg_2017[urg_2017$Idcausa == 23 &
             urg_2017$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_trauma) <-
  c (
    "id",
    "hosp_trauma_all",
    "hosp_trauma_a1",
    "hosp_trauma_1a4",
    "hosp_trauma_5a14",
    "hosp_trauma_15a64",
    "hosp_trauma_65a",
    "date"
  )

# -------- Merge Columns Into One Dataset --------
cons <- merge(cons_total, cons_resp)
cons <- merge(cons, cons_circ)
cons <- merge(cons, cons_diarrea)
cons <- merge(cons, cons_trauma)

hosps <- merge(hosp_total, hosp_resp)
hosps <- merge(hosps, hosp_circ)
hosps <- merge(hosps, hosp_trauma)

urg17_3 <- merge(cons, hosps)

# -------- Write CSV File --------
#write_csv(urg17_3, "urg17_3.csv")
```

```{r 1 - Urg18_3 Data Creation}
# -------- Access Data --------
#rm(list=setdiff(ls(), "dt"))
establecimientos <-
  readr::read_delim("establecimientos.csv",
             ";",
             escape_double = FALSE,
             trim_ws = TRUE)

#d8 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2018.mdb")
#urg_2018 <- sqlFetch(d8, "AtencionesUrgencia2018")
#odbcClose(d8)

target <- tempfile()
file.path(target)
unzip(paste0(getwd(), '/',"AtencionesUrg_18.zip"), exdir = target)
f <- list.files(target, pattern = ".mdb")
d8 <- RODBC::odbcConnectAccess2007(file.path(target, f))
#d5 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2015.mdb")
urg_2018 <- sqlFetch(d8, "AtencionesUrgencia2018")
odbcClose(d8)
unlink(target)

# -------- Establish Hospital ID Codes --------
estab_id <-
  establecimientos[establecimientos$codigo_antiguo == "09-100" |
                     establecimientos$codigo_antiguo == "11-195" |
                     establecimientos$codigo_antiguo == "12-100", "codigo_antiguo", drop =
                     TRUE]
estab_id <- as.factor(estab_id)
columns = c("idestablecimiento",
            "Col01",
            "Col02",
            "Col03",
            "Col04",
            "Col05",
            "Col06",
            "fecha")

# -------- Create Consultation Columns --------
cons_total <-
  urg_2018[urg_2018$Idcausa == 1 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_total) <-
  c (
    "id",
    "cons_total_all",
    "cons_total_a1",
    "cons_total_1a4",
    "cons_total_5a14",
    "cons_total_15a64",
    "cons_total_65a",
    "date"
  )
cons_resp <-
  urg_2018[urg_2018$Idcausa == 2 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_resp) <-
  c (
    "id",
    "cons_resp_all",
    "cons_resp_a1",
    "cons_resp_1a4",
    "cons_resp_5a14",
    "cons_resp_15a64",
    "cons_resp_65a",
    "date"
  )
cons_circ <-
  urg_2018[urg_2018$Idcausa == 12 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_circ) <-
  c (
    "id",
    "cons_circ_all",
    "cons_circ_a1",
    "cons_circ_1a4",
    "cons_circ_5a14",
    "cons_circ_15a64",
    "cons_circ_65a",
    "date"
  )
cons_diarrea <-
  urg_2018[urg_2018$Idcausa == 29 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_diarrea) <-
  c (
    "id",
    "cons_diarrea_all",
    "cons_diarrea_a1",
    "cons_diarrea_1a4",
    "cons_diarrea_5a14",
    "cons_diarrea_15a64",
    "cons_diarrea_65a",
    "date"
  )
cons_trauma <-
  urg_2018[urg_2018$Idcausa == 18 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_trauma) <-
  c (
    "id",
    "cons_trauma_all",
    "cons_trauma_a1",
    "cons_trauma_1a4",
    "cons_trauma_5a14",
    "cons_trauma_15a64",
    "cons_trauma_65a",
    "date"
  )

# -------- Create Hospitalization Columns --------
hosp_total <-
  urg_2018[urg_2018$Idcausa == 25 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_total) <-
  c (
    "id",
    "hosp_total_all",
    "hosp_total_a1",
    "hosp_total_1a4",
    "hosp_total_5a14",
    "hosp_total_15a64",
    "hosp_total_65a",
    "date"
  )
hosp_resp <-
  urg_2018[urg_2018$Idcausa == 7 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_resp) <-
  c (
    "id",
    "hosp_resp_all",
    "hosp_resp_a1",
    "hosp_resp_1a4",
    "hosp_resp_5a14",
    "hosp_resp_15a64",
    "hosp_resp_65a",
    "date"
  )
hosp_circ <-
  urg_2018[urg_2018$Idcausa == 22 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_circ) <-
  c (
    "id",
    "hosp_circ_all",
    "hosp_circ_a1",
    "hosp_circ_1a4",
    "hosp_circ_5a14",
    "hosp_circ_15a64",
    "hosp_circ_65a",
    "date"
  )
hosp_trauma <-
  urg_2018[urg_2018$Idcausa == 23 &
             urg_2018$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_trauma) <-
  c (
    "id",
    "hosp_trauma_all",
    "hosp_trauma_a1",
    "hosp_trauma_1a4",
    "hosp_trauma_5a14",
    "hosp_trauma_15a64",
    "hosp_trauma_65a",
    "date"
  )

# -------- Merge Columns Into One Dataset --------
cons <- merge(cons_total, cons_resp)
cons <- merge(cons, cons_circ)
cons <- merge(cons, cons_diarrea)
cons <- merge(cons, cons_trauma)

hosps <- merge(hosp_total, hosp_resp)
hosps <- merge(hosps, hosp_circ)
hosps <- merge(hosps, hosp_trauma)

urg18_3 <- merge(cons, hosps)

# -------- Write CSV File --------
#write_csv(urg18_3, "urg18_3.csv")
```

```{r 1 - Urg19_3 Data Creation}
# -------- Access Data --------
#rm(list=setdiff(ls(), "dt"))
establecimientos <-
  readr::read_delim("establecimientos.csv",
             ";",
             escape_double = FALSE,
             trim_ws = TRUE)

#d9 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2019.mdb")
#urg_2019 <- sqlFetch(d9, "AtencionesUrgencia2019")
#odbcClose(d9)

target <- tempfile()
file.path(target)
unzip(paste0(getwd(), '/',"AtencionesUrg_19.zip"), exdir = target)
f <- list.files(target, pattern = ".mdb")
d9 <- RODBC::odbcConnectAccess2007(file.path(target, f))
#d5 <- RODBC::odbcConnectAccess2007("AtencionesUrgencia2015.mdb")
urg_2019 <- sqlFetch(d9, "AtencionesUrgencia2019")
odbcClose(d9)
urg_2019$idestablecimiento <- urg_2019$`?idestablecimiento`
unlink(target)

# -------- Establish Hospital ID Codes --------
estab_id <-
  establecimientos[establecimientos$codigo_antiguo == "09-100" |
                     establecimientos$codigo_antiguo == "11-195" |
                     establecimientos$codigo_antiguo == "12-100", "codigo_antiguo", drop =
                     TRUE]
estab_id <- as.factor(estab_id)
columns = c("idestablecimiento",
            "Col01",
            "Col02",
            "Col03",
            "Col04",
            "Col05",
            "Col06",
            "fecha")

# -------- Create Consultation Columns --------
cons_total <-
  urg_2019[urg_2019$Idcausa == 1 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_total) <-
  c (
    "id",
    "cons_total_all",
    "cons_total_a1",
    "cons_total_1a4",
    "cons_total_5a14",
    "cons_total_15a64",
    "cons_total_65a",
    "date"
  )
cons_resp <-
  urg_2019[urg_2019$Idcausa == 2 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_resp) <-
  c (
    "id",
    "cons_resp_all",
    "cons_resp_a1",
    "cons_resp_1a4",
    "cons_resp_5a14",
    "cons_resp_15a64",
    "cons_resp_65a",
    "date"
  )
cons_circ <-
  urg_2019[urg_2019$Idcausa == 12 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_circ) <-
  c (
    "id",
    "cons_circ_all",
    "cons_circ_a1",
    "cons_circ_1a4",
    "cons_circ_5a14",
    "cons_circ_15a64",
    "cons_circ_65a",
    "date"
  )
cons_diarrea <-
  urg_2019[urg_2019$Idcausa == 29 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_diarrea) <-
  c (
    "id",
    "cons_diarrea_all",
    "cons_diarrea_a1",
    "cons_diarrea_1a4",
    "cons_diarrea_5a14",
    "cons_diarrea_15a64",
    "cons_diarrea_65a",
    "date"
  )
cons_trauma <-
  urg_2019[urg_2019$Idcausa == 18 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(cons_trauma) <-
  c (
    "id",
    "cons_trauma_all",
    "cons_trauma_a1",
    "cons_trauma_1a4",
    "cons_trauma_5a14",
    "cons_trauma_15a64",
    "cons_trauma_65a",
    "date"
  )

# -------- Create Hospitalization Columns --------
hosp_total <-
  urg_2019[urg_2019$Idcausa == 25 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_total) <-
  c (
    "id",
    "hosp_total_all",
    "hosp_total_a1",
    "hosp_total_1a4",
    "hosp_total_5a14",
    "hosp_total_15a64",
    "hosp_total_65a",
    "date"
  )
hosp_resp <-
  urg_2019[urg_2019$Idcausa == 7 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_resp) <-
  c (
    "id",
    "hosp_resp_all",
    "hosp_resp_a1",
    "hosp_resp_1a4",
    "hosp_resp_5a14",
    "hosp_resp_15a64",
    "hosp_resp_65a",
    "date"
  )
hosp_circ <-
  urg_2019[urg_2019$Idcausa == 22 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_circ) <-
  c (
    "id",
    "hosp_circ_all",
    "hosp_circ_a1",
    "hosp_circ_1a4",
    "hosp_circ_5a14",
    "hosp_circ_15a64",
    "hosp_circ_65a",
    "date"
  )
hosp_trauma <-
  urg_2019[urg_2019$Idcausa == 23 &
             urg_2019$idestablecimiento %in% estab_id, columns, drop = FALSE]
names(hosp_trauma) <-
  c (
    "id",
    "hosp_trauma_all",
    "hosp_trauma_a1",
    "hosp_trauma_1a4",
    "hosp_trauma_5a14",
    "hosp_trauma_15a64",
    "hosp_trauma_65a",
    "date"
  )

# -------- Merge Columns Into One Dataset --------
cons <- merge(cons_total, cons_resp)
cons <- merge(cons, cons_circ)
cons <- merge(cons, cons_diarrea)
cons <- merge(cons, cons_trauma)

hosps <- merge(hosp_total, hosp_resp)
hosps <- merge(hosps, hosp_circ)
hosps <- merge(hosps, hosp_trauma)

urg19_3 <- merge(cons, hosps)

# -------- Write CSV File --------
#write_csv(urg19_3, "urg19_3.csv")
```

### Format Dates

We generated three variables regarding year, month and day of the date.

```{r 2 - Urg Data Cleaning}
Sys.setlocale(category = "LC_ALL", locale = "english")
`%>%`<- magrittr::`%>%`
# -------- Separate Date into YMD Columns - Urg15 within 3KM --------
urg15_3$date <- as.Date(urg15_3$date, "%d/%m/%Y")
urg15_3 <- urg15_3 %>%
  tidyr::separate(date, sep = "-", into = c("year", "month", "day"))
urg15_3$date <- as.Date(with(urg15_3, paste(year, month, day, sep = "-")))
urg15_3 <- urg15_3[, c(1, 59, 2:4, 5:58)]

# -------- Separate Date into YMD Columns - Urg16 within 3KM --------
urg16_3$date <- as.Date(urg16_3$date, "%d/%m/%Y")
urg16_3 <- urg16_3 %>%
  tidyr::separate(date, sep = "-", into = c("year", "month", "day"))
urg16_3$date <- as.Date(with(urg16_3, paste(year, month, day, sep = "-")))
urg16_3 <- urg16_3[, c(1, 59, 2:4, 5:58)]

# -------- Separate Date into YMD Columns - Urg17 within 3KM --------
urg17_3$date <- as.Date(urg17_3$date, "%d/%m/%Y")
urg17_3 <- urg17_3 %>%
  tidyr::separate(date, sep = "-", into = c("year", "month", "day"))
urg17_3$date <- as.Date(with(urg17_3, paste(year, month, day, sep = "-")))
urg17_3 <- urg17_3[, c(1, 59, 2:4, 5:58)]

# -------- Separate Date into YMD Columns - Urg18 within 3KM --------
urg18_3$date <- as.Date(urg18_3$date, "%d/%m/%Y")
urg18_3 <- urg18_3 %>%
  tidyr::separate(date, sep = "-", into = c("year", "month", "day"))
urg18_3$date <- as.Date(with(urg18_3, paste(year, month, day, sep = "-")))
urg18_3 <- urg18_3[, c(1, 59, 2:4, 5:58)]

# -------- Separate Date into YMD Columns - Urg19 within 3KM --------
urg19_3$date <- as.Date(urg19_3$date, "%d/%m/%Y")
urg19_3 <- urg19_3 %>%
  tidyr::separate(date, sep = "-", into = c("year", "month", "day"))
urg19_3$date <- as.Date(with(urg19_3, paste(year, month, day, sep = "-")))
urg19_3 <- urg19_3[, c(1, 59, 2:4, 5:58)]
```

### Single daily time-series per hospital

We constructed three single time-series databases containing information related to each hospital.

```{r 3 - Time Series (tsdata) Data Creation}
# -------- Isolate urg19_3 Hospital IDs 11-195 & 12-100 --------
# Isolate Hospital ID 09-100
urg19_3$date <- as.Date(urg19_3$date)
urg19_3_09100 <- urg19_3[urg19_3$id == "09-100", ]
urg19_3_09100$year <- as.character(urg19_3_09100$year)
urg19_3_09100 <- urg19_3_09100 %>%
  dplyr::group_by(date) %>%
  dplyr::summarise(
    id = id,
    year = year,
    month = month,
    day = day,
    cons_total_all = cons_total_all,
    cons_total_15a64 = cons_total_15a64,
    cons_total_65a = cons_total_65a,
    cons_resp_all = cons_resp_all,
    cons_resp_15a64 = cons_resp_15a64,
    cons_resp_65a = cons_resp_65a,
    cons_circ_all = cons_circ_all,
    cons_circ_15a64 = cons_circ_15a64,
    cons_circ_65a = cons_circ_65a,
    cons_diarrea_all = cons_diarrea_all,
    cons_diarrea_15a64 = cons_diarrea_15a64,
    cons_diarrea_65a = cons_diarrea_65a,
    cons_trauma_all = cons_trauma_all,
    cons_trauma_15a64 = cons_trauma_15a64,
    cons_trauma_65a = cons_trauma_65a,
    hosp_total_all = hosp_total_all,
    hosp_total_15a64 = hosp_total_15a64,
    hosp_total_65a = hosp_total_65a,
    hosp_resp_all = hosp_resp_all,
    hosp_resp_15a64 = hosp_resp_15a64,
    hosp_resp_65a = hosp_resp_65a,
    hosp_circ_all = hosp_circ_all,
    hosp_circ_15a64 = hosp_circ_15a64,
    hosp_circ_65a = hosp_circ_65a,
    hosp_trauma_all = hosp_trauma_all,
    hosp_trauma_15a64 = hosp_trauma_15a64,
    hosp_trauma_65a = hosp_trauma_65a
  )
urg19_3_09100 <- urg19_3_09100[, c(2, 1, 3:32)]

# Isolate Hospital ID 11-195
urg19_3_11195 <- urg19_3[urg19_3$id == "11-195", ]
urg19_3_11195$year <- as.character(urg19_3_11195$year)
urg19_3_11195 <- urg19_3_11195 %>%
  dplyr::group_by(date) %>%
  dplyr::summarise(
    id = id,
    year = year,
    month = month,
    day = day,
    cons_total_all = cons_total_all,
    cons_total_15a64 = cons_total_15a64,
    cons_total_65a = cons_total_65a,
    cons_resp_all = cons_resp_all,
    cons_resp_15a64 = cons_resp_15a64,
    cons_resp_65a = cons_resp_65a,
    cons_circ_all = cons_circ_all,
    cons_circ_15a64 = cons_circ_15a64,
    cons_circ_65a = cons_circ_65a,
    cons_diarrea_all = cons_diarrea_all,
    cons_diarrea_15a64 = cons_diarrea_15a64,
    cons_diarrea_65a = cons_diarrea_65a,
    cons_trauma_all = cons_trauma_all,
    cons_trauma_15a64 = cons_trauma_15a64,
    cons_trauma_65a = cons_trauma_65a,
    hosp_total_all = hosp_total_all,
    hosp_total_15a64 = hosp_total_15a64,
    hosp_total_65a = hosp_total_65a,
    hosp_resp_all = hosp_resp_all,
    hosp_resp_15a64 = hosp_resp_15a64,
    hosp_resp_65a = hosp_resp_65a,
    hosp_circ_all = hosp_circ_all,
    hosp_circ_15a64 = hosp_circ_15a64,
    hosp_circ_65a = hosp_circ_65a,
    hosp_trauma_all = hosp_trauma_all,
    hosp_trauma_15a64 = hosp_trauma_15a64,
    hosp_trauma_65a = hosp_trauma_65a
  )
urg19_3_11195 <- urg19_3_11195[, c(2, 1, 3:32)]

# Isolate Hospital ID 12-100
urg19_3_12100 <- urg19_3[urg19_3$id == "12-100", ]
urg19_3_12100$year <- as.character(urg19_3_12100$year)
urg19_3_12100 <- urg19_3_12100 %>%
  dplyr::group_by(date) %>%
  dplyr::summarise(
    id = id,
    year = year,
    month = month,
    day = day,
    cons_total_all = cons_total_all,
    cons_total_15a64 = cons_total_15a64,
    cons_total_65a = cons_total_65a,
    cons_resp_all = cons_resp_all,
    cons_resp_15a64 = cons_resp_15a64,
    cons_resp_65a = cons_resp_65a,
    cons_circ_all = cons_circ_all,
    cons_circ_15a64 = cons_circ_15a64,
    cons_circ_65a = cons_circ_65a,
    cons_diarrea_all = cons_diarrea_all,
    cons_diarrea_15a64 = cons_diarrea_15a64,
    cons_diarrea_65a = cons_diarrea_65a,
    cons_trauma_all = cons_trauma_all,
    cons_trauma_15a64 = cons_trauma_15a64,
    cons_trauma_65a = cons_trauma_65a,
    hosp_total_all = hosp_total_all,
    hosp_total_15a64 = hosp_total_15a64,
    hosp_total_65a = hosp_total_65a,
    hosp_resp_all = hosp_resp_all,
    hosp_resp_15a64 = hosp_resp_15a64,
    hosp_resp_65a = hosp_resp_65a,
    hosp_circ_all = hosp_circ_all,
    hosp_circ_15a64 = hosp_circ_15a64,
    hosp_circ_65a = hosp_circ_65a,
    hosp_trauma_all = hosp_trauma_all,
    hosp_trauma_15a64 = hosp_trauma_15a64,
    hosp_trauma_65a = hosp_trauma_65a
  )
urg19_3_12100 <- urg19_3_12100[, c(2, 1, 3:32)]

# Re-Bind Data with only ID 09-100, 11-195 & 12-100
urg19_3_clean <- rbind(urg19_3_09100, urg19_3_11195, urg19_3_12100)

# -------- Control Dataset - 3KM --------
urg_control_3 <- rbind(urg15_3, urg16_3, urg17_3, urg18_3)
```

### Sum of daily counts of hospitalizations and consultations

We generated an aggregated database containing the sum of daily counts of each type of consultation and hospitalization.

```{r 4 - Time Series (tsdata) Data Cleaning}
# -------- Sum Hospital ID Cases - urg19_3_clean --------
urg19_3_clean$date <- as.Date(urg19_3_clean$date)

urg19_3_clean_cons <- urg19_3_clean %>%
  dplyr::group_by(date) %>%
  dplyr::summarise(
    year = unique(year),
    month = unique(month),
    day = unique(day),
    cons_total_all = sum(cons_total_all),
    cons_total_15a64 = sum(cons_total_15a64),
    cons_total_65a = sum(cons_total_65a),
    cons_resp_all = sum(cons_resp_all),
    cons_resp_15a64 = sum(cons_resp_15a64),
    cons_resp_65a = sum(cons_resp_65a),
    cons_circ_all = sum(cons_circ_all),
    cons_circ_15a64 = sum(cons_circ_15a64),
    cons_circ_65a = sum(cons_circ_65a),
    cons_diarrea_all = sum(cons_diarrea_all),
    cons_diarrea_15a64 = sum(cons_diarrea_15a64),
    cons_diarrea_65a = sum(cons_diarrea_65a),
    cons_trauma_all = sum(cons_trauma_all),
    cons_trauma_15a64 = sum(cons_trauma_15a64),
    cons_trauma_65a = sum(cons_trauma_65a),
    hosp_total_all = sum(hosp_total_all),
    hosp_total_15a64 = sum(hosp_total_15a64),
    hosp_total_65a = sum(hosp_total_65a),
    hosp_resp_all = sum(hosp_resp_all),
    hosp_resp_15a64 = sum(hosp_resp_15a64),
    hosp_resp_65a = sum(hosp_resp_65a),
    hosp_circ_all = sum(hosp_circ_all),
    hosp_circ_15a64 = sum(hosp_circ_15a64),
    hosp_circ_65a = sum(hosp_circ_65a),
    hosp_trauma_all = sum(hosp_trauma_all),
    hosp_trauma_15a64 = sum(hosp_trauma_15a64),
    hosp_trauma_65a = sum(hosp_trauma_65a)
  )
# -------- Sum Hospital ID Cases - tsdata3 --------
urg_control_3$date <- as.Date(urg_control_3$date)
#tsdata3=urg_control_3
tsdata3 <- urg_control_3 %>%
  dplyr::group_by(date) %>%
  dplyr::summarise(
    year = unique(year),
    month = unique(month),
    day = unique(day),
    cons_total_all = sum(cons_total_all),
    cons_total_15a64 = sum(cons_total_15a64),
    cons_total_65a = sum(cons_total_65a),
    cons_resp_all = sum(cons_resp_all),
    cons_resp_15a64 = sum(cons_resp_15a64),
    cons_resp_65a = sum(cons_resp_65a),
    cons_circ_all = sum(cons_circ_all),
    cons_circ_15a64 = sum(cons_circ_15a64),
    cons_circ_65a = sum(cons_circ_65a),
    cons_diarrea_all = sum(cons_diarrea_all),
    cons_diarrea_15a64 = sum(cons_diarrea_15a64),
    cons_diarrea_65a = sum(cons_diarrea_65a),
    cons_trauma_all = sum(cons_trauma_all),
    cons_trauma_15a64 = sum(cons_trauma_15a64),
    cons_trauma_65a = sum(cons_trauma_65a),
    hosp_total_all = sum(hosp_total_all),
    hosp_total_15a64 = sum(hosp_total_15a64),
    hosp_total_65a = sum(hosp_total_65a),
    hosp_resp_all = sum(hosp_resp_all),
    hosp_resp_15a64 = sum(hosp_resp_15a64),
    hosp_resp_65a = sum(hosp_resp_65a),
    hosp_circ_all = sum(hosp_circ_all),
    hosp_circ_15a64 = sum(hosp_circ_15a64),
    hosp_circ_65a = sum(hosp_circ_65a),
    hosp_trauma_all = sum(hosp_trauma_all),
    hosp_trauma_15a64 = sum(hosp_trauma_15a64),
    hosp_trauma_65a = sum(hosp_trauma_65a)
  )

```

### Analyse shocks

```{r exp_plot_lines1, echo=T, cache= T, paged.print=TRUE, warning=F, fig.height=14,eval=T, fig.align='center', fig.cap= "Figure 1. No. of Days with 0 hospitalizations in 2018 (from 15 to 64 years)\nby Cause and Institution"}
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#PLOT TO SHOW HOW WE STABILIZED SHOCKS ON 2018

 urg_control_3 %>% 
   dplyr::filter(year==2018) %>% 
  dplyr::mutate(date2=readr::parse_datetime(as.character(date), "%Y-%m-%d")) %>% 
  dplyr::mutate(fech_week=format(date2,'%V')) %>%
    dplyr::mutate(id=factor(id, labels= c("Complejo Hospitalario San Jose (09-100)", 
                                          "Hospital de Urgencia Asistencia Publica (11-195)", 
                                          "Hospital Del Salvador de Santiago (12-100)"))) %>% 
     pivot_longer(cols=cons_total_all:hosp_trauma_65a, names_to = "variable", values_to = "count") %>% 
    dplyr::filter(variable  %in% c("hosp_total_15a64","hosp_resp_15a64","hosp_circ_15a64","hosp_trauma_15a64")) %>% 
    dplyr::filter(count==0) %>%
    dplyr::group_by(id,fech_week,variable) %>% 
    dplyr::summarise(n = as.numeric(n()), start=min(date2)) %>% 
   dplyr::ungroup() %>% 
    ggplot2::ggplot(aes(x = fech_week, y = n, color=variable,group=variable)) +
    geom_point(size=1.5) +
    geom_line(alpha=.5) +
    facet_wrap(id~.,ncol=1)+
    #ylim()+
    scale_color_manual("Hospitalizations", values=c("red", "blue", "green", "violet"), labels = c("Circulatory", "Respiratory","Total","Trauma")) +
    sjPlot::theme_sjplot2() +
    scale_y_continuous(breaks = c(0,1,2,3,4,5,6,7,8),limits=c(0,8))+
    labs(y="No. of Days in the week with 0 counts",
         x="Years & Weeks") + 
    theme(axis.text.x = element_text(vjust = 0.5,hjust = 0.5,angle = 60), plot.caption=element_text(hjust=0)) 

```

<br>

Aa seen in Figure 1, HUAP(11-195) had 2 important periods with weeks of 0 hospitlizations. These shocks may confound the posterior results, so we decided to interpolate these numbers with the median of 2018 of every institution.

<br>

```{r datasets_cons0, echo=T, cache= T, paged.print=TRUE, warning=F}
#tsdata3 <- read.csv("tsdata3.csv")

#tsdata3 %>% glimpse()  # hosp_resp_ hosp_circ_ hosp_trauma_ hosp_total_
tsdata3_corr<-
urg_control_3 %>% 
  dplyr::mutate(date2=readr::parse_datetime(as.character(date), "%Y-%m-%d")) %>% 
  dplyr::mutate(fech_week=format(date2,'%V')) %>%
  dplyr::arrange(id,fech_week)%>%
  
  dplyr::mutate(hosp_resp_all= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_resp_all))%>%
  dplyr::mutate(hosp_resp_15a64= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_resp_15a64))%>% 
  dplyr::mutate(hosp_resp_65a= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_resp_65a))%>%
  
  dplyr::mutate(hosp_circ_all= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_circ_all))%>%  
  dplyr::mutate(hosp_circ_15a64= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_circ_15a64))%>% 
  dplyr::mutate(hosp_circ_65a= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_circ_65a))%>%
  
  dplyr::mutate(hosp_trauma_all= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_trauma_all))%>%   
    dplyr::mutate(hosp_trauma_15a64= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_trauma_15a64))%>%
  dplyr::mutate(hosp_trauma_65a= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_trauma_65a))%>%
  
  dplyr::mutate(hosp_total_all= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_total_all))%>%   dplyr::mutate(hosp_total_15a64= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_total_15a64))%>%   
  dplyr::mutate(hosp_total_65a= dplyr::case_when(id=="11-195" & year==2018 & fech_week %in% c(10,11,25,26)~NA_integer_, TRUE~hosp_total_65a))%>%
  
  dplyr::group_by(id,year) %>% 
 ### REPLACE WITH THE MEAN 
    dplyr::mutate(hosp_resp_all= zoo::na.aggregate(hosp_resp_all,FUN=median))%>% 
  dplyr::mutate(hosp_resp_15a64= zoo::na.aggregate(hosp_resp_15a64,FUN=median))%>%   #na.locf(x,fromLast = FALSE) #nearest non-NA value
  dplyr::mutate(hosp_resp_65a= zoo::na.aggregate(hosp_resp_65a,FUN=median))%>%   #na.aggregate(dat,FUN = mean) #linear= na.approx
  
    dplyr::mutate(hosp_circ_all= zoo::na.aggregate(hosp_circ_all,FUN=median))%>% 
  dplyr::mutate(hosp_circ_15a64= zoo::na.aggregate(hosp_circ_15a64,FUN=median))%>%   #na.locf(x,fromLast = FALSE) #nearest non-NA value
  dplyr::mutate(hosp_circ_65a= zoo::na.aggregate(hosp_circ_65a,FUN=median))%>%   #na.aggregate(dat,FUN = mean) #linear= na.approx
  
    dplyr::mutate(hosp_trauma_all= zoo::na.aggregate(hosp_trauma_all,FUN=median))%>% 
  dplyr::mutate(hosp_trauma_15a64= zoo::na.aggregate(hosp_trauma_15a64,FUN=median))%>%   #na.locf(x,fromLast = FALSE) #nearest non-NA value
  dplyr::mutate(hosp_trauma_65a= zoo::na.aggregate(hosp_trauma_65a,FUN=median))%>%   #na.aggregate(dat,FUN = mean) #linear= na.approx
  
    dplyr::mutate(hosp_total_all= zoo::na.aggregate(hosp_total_all,FUN=median))%>% 
  dplyr::mutate(hosp_total_15a64= zoo::na.aggregate(hosp_total_15a64,FUN=median))%>%   #na.locf(x,fromLast = FALSE) #nearest non-NA value
  dplyr::mutate(hosp_total_65a= zoo::na.aggregate(hosp_total_65a,FUN=median))%>%   #na.aggregate(dat,FUN = mean) #linear= na.approx
  dplyr::ungroup() %>% 
  dplyr::select(-date2,-fech_week)

tsdata3_corr_cons <- tsdata3_corr %>%
  dplyr::group_by(date) %>%
  dplyr::summarise(
    year = unique(year),
    month = unique(month),
    day = unique(day),
    cons_total_all = sum(cons_total_all),
    cons_total_15a64 = sum(cons_total_15a64),
    cons_total_65a = sum(cons_total_65a),
    cons_resp_all = sum(cons_resp_all),
    cons_resp_15a64 = sum(cons_resp_15a64),
    cons_resp_65a = sum(cons_resp_65a),
    cons_circ_all = sum(cons_circ_all),
    cons_circ_15a64 = sum(cons_circ_15a64),
    cons_circ_65a = sum(cons_circ_65a),
    cons_diarrea_all = sum(cons_diarrea_all),
    cons_diarrea_15a64 = sum(cons_diarrea_15a64),
    cons_diarrea_65a = sum(cons_diarrea_65a),
    cons_trauma_all = sum(cons_trauma_all),
    cons_trauma_15a64 = sum(cons_trauma_15a64),
    cons_trauma_65a = sum(cons_trauma_65a),
    hosp_total_all = sum(hosp_total_all),
    hosp_total_15a64 = sum(hosp_total_15a64),
    hosp_total_65a = sum(hosp_total_65a),
    hosp_resp_all = sum(hosp_resp_all),
    hosp_resp_15a64 = sum(hosp_resp_15a64),
    hosp_resp_65a = sum(hosp_resp_65a),
    hosp_circ_all = sum(hosp_circ_all),
    hosp_circ_15a64 = sum(hosp_circ_15a64),
    hosp_circ_65a = sum(hosp_circ_65a),
    hosp_trauma_all = sum(hosp_trauma_all),
    hosp_trauma_15a64 = sum(hosp_trauma_15a64),
    hosp_trauma_65a = sum(hosp_trauma_65a)
  )
```

```{r exp_plot_lines, echo=T, cache= T, paged.print=TRUE, warning=F, fig.height=14,eval=T, fig.align='center', fig.cap= "Figure 2. No. of Days with 0 hospitalizations in 2018 (from 15 to 64 years)\nby Cause and Institution, After Interpolaiton"}
#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_#_
#PLOT TO SHOW HOW WE STABILIZED SHOCKS ON 2018

 tsdata3_corr %>% 
   dplyr::filter(year==2018) %>% 
  dplyr::mutate(date2=readr::parse_datetime(as.character(date), "%Y-%m-%d")) %>% 
  dplyr::mutate(fech_week=format(date2,'%V')) %>%
    dplyr::mutate(id=factor(id, labels= c("Complejo Hospitalario San Jose (09-100)", 
                                          "Hospital de Urgencia Asistencia Publica (11-195)", 
                                          "Hospital Del Salvador de Santiago (12-100)"))) %>% 
     pivot_longer(cols=cons_total_all:hosp_trauma_65a, names_to = "variable", values_to = "count") %>% 
    dplyr::filter(variable  %in% c("hosp_total_15a64","hosp_resp_15a64","hosp_circ_15a64","hosp_trauma_15a64")) %>% 
    dplyr::filter(count==0) %>%
    dplyr::group_by(id,fech_week,variable) %>% 
    dplyr::summarise(n = as.numeric(n()), start=min(date2)) %>% 
   dplyr::ungroup() %>% 
    ggplot2::ggplot(aes(x = fech_week, y = n, color=variable,group=variable)) +
    geom_point(size=1.5) +
    geom_line(alpha=.5) +
    facet_wrap(id~.,ncol=1)+
    #ylim()+
    scale_color_manual("Hospitalizations", values=c("red", "blue", "green", "violet"), labels = c("Circulatory", "Respiratory","Total","Trauma")) +
    sjPlot::theme_sjplot2() +
    scale_y_continuous(breaks = c(0,1,2,3,4,5,6,7,8),limits=c(0,8))+
    labs(y="No. of Days in the week with 0 counts",
         x="Years & Weeks") + 
    theme(axis.text.x = element_text(vjust = 0.5,hjust = 0.5,angle = 60), plot.caption=element_text(hjust=0)) 
```
<br>

As seen in Figure 2, the interpolation resulted in stabilized counts of hospitaizations in 2018.

<br>

### Group values by week

In first place, we downloaded the data and defined the datasets.

<br>

```{r datasets_cons1, echo=T, cache= T, paged.print=TRUE, warning=F}
########## Read Data from CSV File ########
data.control_corr <- tsdata3_corr_cons
data.tx <- urg19_3_clean_cons
data <- rbind(data.control_corr, data.tx)
data$year_week <- strftime(as.Date(data$date), format = "%Y-W%V")
remove(data.control)
remove(data.tx)

########## Create Dummy Variables ########
#aquí agrupó las instituciones
## Dummy Variables for Age Group ##
data15a64 <- data %>%
  group_by(date) %>%
  summarise(
    year = year,
    month = month,
    day = day,
    cons_total = cons_total_15a64,
    cons_resp = cons_resp_15a64,
    cons_circ = cons_circ_15a64,
    cons_diarrea = cons_diarrea_15a64,
    cons_trauma = cons_trauma_15a64,
    hosp_total = hosp_total_15a64,
    hosp_resp = hosp_resp_15a64,
    hosp_circ = hosp_circ_15a64,
    hosp_trauma = hosp_trauma_15a64,
    age = "15-64"
  )

data65a <- data %>%
  group_by(date) %>%
  summarise(
    year = year,
    month = month,
    day = day,
    cons_total = cons_total_65a,
    cons_resp = cons_resp_65a,
    cons_circ = cons_circ_65a,
    cons_diarrea = cons_diarrea_65a,
    cons_trauma = cons_trauma_65a,
    hosp_total = hosp_total_65a,
    hosp_resp = hosp_resp_65a,
    hosp_circ = hosp_circ_65a,
    hosp_trauma = hosp_trauma_65a,
    age = "65+"
  )

data <- rbind(data15a64, data65a)
data$year_week <- strftime(as.Date(data$date), format = "%Y-W%V")
data$age <- as.factor(data$age)
remove(data15a64)
remove(data65a)

## Other Dummy Variables ##
data$exptime <- ifelse(data$month >=8, 1, 0)
data$txtime <- ifelse(data$month >= 10 & data$day >= 18 | data$month >= 11, 1, 0)
data$tx <- ifelse(data$year == "2019", 1, 0)
data$did <- data$txtime * data$tx

data$time <- 0
data$time[data$exptime == 1] <- seq(by = 1, from = 1, to = 153)
data$post <- 0
data$post[data$did == 1] <- seq(by = 1, to = 87) #no me funciona length(data$post[data$did == 1])= 150 
Sys.setlocale(category = "LC_ALL", locale = "english")
#por qué no me funciona: data15a64%>% dplyr::filter(date>="2019-10-18")%>% dplyr::summarise(min=min(time),max=max(time),diff=max-min)


#:#:#::#:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:
#:#:#::#:##:#:#:#:#:
#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:#:#:#::#:##:#:#:#:#:

invisible(c("lo tuve que sacar"))

#data <- data[data$date != "2016-02-29", ]

data$yearday <- strftime(as.Date(data$date), format = "%j")
data$yearday <- as.numeric(data$yearday)
#data$yearday[data$year == 2016 & data$date > as.Date("2016-02-28")] <- data$yearday[data$year == 2016 & data$date > as.Date("2016-02-28")] - 1
#glimpse(data)
Sys.setlocale(category = "LC_ALL", locale = "english")
data$weekday <- weekdays(as.Date(data$date))
data$weekday <- ordered(data$weekday, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))

data$sig <- ifelse(data$month == 10 & data$day == 6 | data$month == 10 & data$day == 18 | data$month == 10 & data$day == 25, 1, 0)
data$week <-lubridate::week(data$date)
data$isoweek <-lubridate::isoweek(lubridate::ymd(data$date))

#lubridate::floor_date(isoweek(data$date, "%Y-%m-%d"), unit="week")

## Dummy Variable for Dependent Variable of Choice Prior Day Value ##
data$prevtrc[data$age == "15-64"] <- c(NA, data$cons_trauma[data$age == "15-64"][-1825])
data$prevtrc[data$age == "65+"] <- c(NA, data$cons_trauma[data$age == "65+"][-1825])
data$prevrec[data$age == "15-64"] <- c(NA, data$cons_resp[data$age == "15-64"][-1825])
data$prevrec[data$age == "65+"] <- c(NA, data$cons_resp[data$age == "65+"][-1825])
data$prevtrh[data$age == "15-64"] <- c(NA, data$hosp_trauma[data$age == "15-64"][-1825])
data$prevtrh[data$age == "65+"] <- c(NA, data$hosp_trauma[data$age == "65+"][-1825])
data$prevreh[data$age == "15-64"] <- c(NA, data$hosp_resp[data$age == "15-64"][-1825])
data$prevreh[data$age == "65+"] <- c(NA, data$hosp_resp[data$age == "65+"][-1825])

########## Create Dummy Variables ########
#aquí agrupó las instituciones
## Dummy Variables for Age Group ##
data15a64_wk <- data %>%
  dplyr::filter(as.character(age)=="15-64")%>%
  dplyr::group_by(year_week) %>%
  summarise(
    year = year,
    month = month,
    day = day,
    date= date,
    cons_total = sum(cons_total,na.rm=T),
    cons_resp = sum(cons_resp,na.rm=T),
    cons_circ = sum(cons_circ,na.rm=T),
    cons_diarrea = sum(cons_diarrea,na.rm=T),
    cons_trauma = sum(cons_trauma,na.rm=T),
    hosp_total = sum(hosp_total,na.rm=T),
    hosp_resp = sum(hosp_resp,na.rm=T),
    hosp_circ = sum(hosp_circ,na.rm=T),
    hosp_trauma = sum(hosp_trauma,na.rm=T),
    sig= sig,
    weekday= weekday,
    yearday= yearday,
    prevtrc= sum(prevtrc,na.rm=T),
    prevrec= sum(prevrec,na.rm=T),
    prevtrh= sum(prevtrh,na.rm=T),
    prevreh= sum(prevreh,na.rm=T),
    week=week,
    isoweek=isoweek
    )%>%
  slice(1)%>%
  ungroup()

data65a_wk <- data %>%
  dplyr::filter(as.character(age)=="65+")%>%
  dplyr::group_by(year_week)%>%
  summarise(
    year = year,
    month = month,
    day = day,
    date= date,
    cons_total = sum(cons_total,na.rm=T),
    cons_resp = sum(cons_resp,na.rm=T),
    cons_circ = sum(cons_circ,na.rm=T),
    cons_diarrea = sum(cons_diarrea,na.rm=T),
    cons_trauma = sum(cons_trauma,na.rm=T),
    hosp_total = sum(hosp_total,na.rm=T),
    hosp_resp = sum(hosp_resp,na.rm=T),
    hosp_circ = sum(hosp_circ,na.rm=T),
    hosp_trauma = sum(hosp_trauma,na.rm=T),
    sig= sig,
    weekday= weekday,
    yearday= yearday,
    prevtrc= sum(prevtrc,na.rm=T),
    prevrec= sum(prevrec,na.rm=T),
    prevtrh= sum(prevtrh,na.rm=T),
    prevreh= sum(prevreh,na.rm=T),
    week=week,
    isoweek=isoweek
  )%>%
  slice(1)%>%
  ungroup()

data15a64_wk$difftrc <- data15a64_wk$cons_total - data15a64_wk$cons_trauma
data15a64_wk$difftrh <- data15a64_wk$hosp_total - data15a64_wk$hosp_trauma
data15a64_wk$diffrec <- data15a64_wk$cons_total - data15a64_wk$cons_resp
data15a64_wk$diffreh <- data15a64_wk$hosp_total - data15a64_wk$hosp_resp

data15a64_wk$offset <- data15a64_wk$cons_total + data15a64_wk$hosp_total

data65a_wk$difftrc <- data65a_wk$cons_total - data65a_wk$cons_trauma
data65a_wk$difftrh <- data65a_wk$hosp_total - data65a_wk$hosp_trauma
data65a_wk$diffrec <- data65a_wk$cons_total - data65a_wk$cons_resp
data65a_wk$diffreh <- data65a_wk$hosp_total - data65a_wk$hosp_resp

data65a_wk$offset <- data65a_wk$cons_total + data65a_wk$hosp_total

#data$tx <- ifelse(data$year == "2019", 1, 0)
#data$did <- data$txtime * data$tx
data15a64_wk$txtime <- ifelse(data15a64_wk$year == 2019 & data15a64_wk$isoweek>42, 1, 0)
data15a64_wk$txtime2 <- ifelse(data15a64_wk$year == 2019 & data15a64_wk$isoweek>41, 1, 0)
data15a64_wk$tx <- ifelse(data15a64_wk$year == 2019, 1, 0)
data15a64_wk$did <- data15a64_wk$txtime * data15a64_wk$tx

data65a_wk$txtime <- ifelse(data65a_wk$year == 2019 & data65a_wk$isoweek>42, 1, 0)
data65a_wk$txtime2 <- ifelse(data65a_wk$year == 2019 & data65a_wk$isoweek>41, 1, 0)
data65a_wk$tx <- ifelse(data65a_wk$year == 2019, 1, 0)
data65a_wk$did <- data65a_wk$txtime * data65a_wk$tx
#2019-W42

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

data15a64_rn<- data15a64_wk%>% dplyr::mutate(rn=row_number())

data15a64_rn_ratio<- data15a64_rn %>% 
  dplyr::mutate(rate=(hosp_trauma/cons_trauma)*1000) %>% 
  dplyr::mutate(ratio=hosp_trauma/cons_trauma) %>% 
  dplyr::mutate(ratio_circ=hosp_circ/cons_circ) %>% 
  dplyr::mutate(rate_circ=(hosp_circ/cons_circ)*1000) %>% 
  dplyr::mutate(rate_resp=(hosp_resp/cons_resp)*1000) %>% 
  dplyr::mutate(ratio_resp=hosp_resp/cons_resp)

attr(data15a64_rn_ratio$ratio,"variable.labels") <- "Ratio Between Trauma Hospitalizations and Trauma Consultations"
attr(data15a64_rn_ratio$rate,"variable.labels") <- "Rate of Trauma Hospitalizations per Trauma Consultations per 1,000 population"
attr(data15a64_rn_ratio$rate,"variable.labels") <- "Rate of Trauma Hospitalizations per Trauma Consultations per 1,000 population"
attr(data15a64_rn_ratio$year_week, "label") <- "Year-Week (ISO 8601) (chr)"
attr(data15a64_rn_ratio$isoweek, "label") <- "Week Number (ISO 8601) (num)"
attr(data15a64_rn_ratio$year, "label") <- "Year"
attr(data15a64_rn_ratio$month, "label") <- "Month"
attr(data15a64_rn_ratio$day, "label") <- "Day"

attr(data15a64_rn_ratio$cons_total, "label") <- "Total Consultations"
attr(data15a64_rn_ratio$cons_resp, "label") <- "Respiratory Consultations"
attr(data15a64_rn_ratio$cons_circ, "label") <- "Circulatory Consultations"
attr(data15a64_rn_ratio$cons_diarrea, "label") <- "Diarrhea Consultations"
attr(data15a64_rn_ratio$cons_trauma, "label") <- "Trauma Consultations"

attr(data15a64_rn_ratio$hosp_total, "label") <- "Total Hospitalizations"
attr(data15a64_rn_ratio$hosp_resp, "label") <- "Respiratory Hospitalizations"
attr(data15a64_rn_ratio$hosp_circ, "label") <- "Circulatory Hospitalizations"
attr(data15a64_rn_ratio$hosp_trauma, "label") <- "Trauma Hospitalizations"

#attr(data$age, "label") <- "Age (factor)"
#attr(data$exptime, "label") <- "From August 8th to December 31th"
#attr(data15a64_wk) <- "Treatment Period"
attr(data15a64_rn_ratio$tx, "label") <- "Post-treatment Period (Only 2019)"
attr(data15a64_rn_ratio$did, "label") <- "Post-Treatment Period * Treatment"
#attr(data15a64_wk$time, "label") <- "August 1st to December 31th, by Year"
attr(data15a64_rn_ratio$txtime2, "label") <- "Post-intervention Period (After but incluiding 2019-10-18 W42)"
attr(data15a64_rn_ratio$txtime, "label") <- "Post-intervention Period (After 2019-10-18 W42)"
attr(data15a64_rn_ratio$yearday, "label") <- "Day of the year (numeric)"
attr(data15a64_rn_ratio$weekday, "label") <- "Weekday"
attr(data15a64_rn_ratio$week, "label") <- "Week number by Year (Lubridate criteria)"  #no está presente

attr(data15a64_rn_ratio$sig, "label") <- "October 6th; October 18th; October 25th"

attr(data15a64_rn_ratio$prevtrc, "label") <- "Dependent Variable of Choice Prior Day Value of the Total Trauma Consultations"
attr(data15a64_rn_ratio$prevrec, "label") <-  "Dependent Variable of Choice Prior Day Value of the Total Respiratory Consultations"
attr(data15a64_rn_ratio$prevtrh, "label") <- "Dependent Variable of Choice Prior Day Value of the Total Trauma Hospitalizations"
attr(data15a64_rn_ratio$prevreh, "label") <- "Dependent Variable of Choice Prior Day Value of the Total Respiratory Hospitalizations"

attr(data15a64_rn_ratio$difftrc, "label") <- "Difference Between Total Consultations and the Total Trauma Consultations"
attr(data15a64_rn_ratio$difftrh, "label") <- "Difference Between Total Hospitalizations and the Total Trauma Hospitalizations"
attr(data15a64_rn_ratio$diffrec, "label") <-  "Difference Between Total Consultations and the Total Respiratory Consultations"
attr(data15a64_rn_ratio$diffreh, "label") <- "Difference Between Total Hospitalizations and the Total Respiratory Hospitalizations"
attr(data15a64_rn_ratio$offset, "label") <- "Sum of the total consultations and total hospitalizations"

attr(data15a64_rn_ratio$rate,"label") <- "Rate of Trauma Hospitalizations per Trauma Consultations (x1,000 population)"
attr(data15a64_rn_ratio$rate_resp,"label") <- "Respiratory Hospitalizations per Respiratory Consultations (x1,000 population)"

library(compareGroups)
#pvals <- compareGroups::getResults(table, "p.overall")
table2 <- compareGroups::compareGroups(did ~ cons_total+ cons_trauma+ cons_resp+ cons_circ+ hosp_total+ hosp_trauma+ hosp_resp+ hosp_circ+ rate+ rate_resp, #27
                       method = c(cons_total=2, cons_trauma=2, cons_resp=2, cons_circ=2,  hosp_total=2,
                                  hosp_resp=2, hosp_circ=2, hosp_trauma=2,rate=2, rate_resp=2),
                      data = data15a64_rn_ratio,
                      include.miss = T,
                      var.equal=T)
                      #,
                      #subset = age == "15-64")
#p.adjust(pvals, method = "BH")
restab <- createTable(table2, show.n = F, show.p.overall = F)
 compareGroups::export2md(restab, first.strip = T, show.all = T,hide.no = "no",header.labels = c(`0`= "Pre- Oct 18, 2020", `1`="Post Oct 18, 2020"), size=12,col.names= c("", "Previous to social
protests","During social protests"),format="html",position="center",caption= "Table 1. Median descriptive table of emergency department consultations and hospitalizations, pre and port Ocober’s 2019 social protests in Chile")%>%#,p.overall = "p-value"
  kableExtra::add_footnote(paste0("Note. Percentiles 25 and 75 in brackets."), notation = "none")%>%
  kableExtra::scroll_box(width = "100%", height = "375px")
```

<br>

We subsetted the interval of consultations and hospitalizations of patients between 15 and 64.

<br>

# Session Info

```{r save, echo=T, cache= T, paged.print=TRUE, warning=F, eval=T}
Sys.getenv("R_LIBS_USER")

rstudioapi::getSourceEditorContext()

#paste0("Folder where packages were saved: ",get.groundhog.folder())

sessionInfo()

save.image(paste0(getwd(),"/","Procesos hasta 4_2.RData"))

```
